Unit tests

### 2018-03-09 Tests.Rmd
Editorial changes to Tests.Rmd

# Test flexible copula functions

@@

Test the cor statistic:
```{r test_copula_function_flexible_cor, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
plot_vivj(vi,vj,lb,ub)
h<-Corbds(vi,vj,lb=lb,ub=ub)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

@@

Test the D2 statistic:
```{r test_copula_function_flexible_D2, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-D2bds(vi,vj,lb=lb,ub=ub)
if (abs((sum(ep[1:4]^2)/2)-h)<1e-12)
{
  print("passed")
}
```

Test the P statistic:
```{r test_copula_function_flexible_P, echo=T}
source("CopulaFunctions_flexible.R")

@@

#Test for when two parallel boundary lines are on the left side of vi+vj=1 line
lb=0
ub=.45
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)
hl<-Pbds(vi,vj,lb=lb,ub=ub)

#plot the step fn
plot(hl$dist_S,hl$S,type="b")

#calculate the area under the curve 
vertices<-unique(hl$dist_S[(hl$dist_S!=0)])
area_S<-(vertices[2]-vertices[1])*1
area_S

area_S==hl$Au_S # it's a check

hl$Au_Si

#P stat value for lower tail
(area_S-hl$Au_Si)==hl$abs_res

#Test for when two parallel boundary lines are on the right side of vi+vj=1 line
lb=0
ub=.4 # if ub=0.45 then hu$Au_Si = hl$Au_Si : so, it's a check on Au_Si
plot_vivj(vi=vi,vj=vj,lb=(1-ub),ub=(1-lb))

@@

#plot the step fn
plot(hu$dist_S,hu$S,type="b")

#calculate the area under the curve 
w1<-unique(hu$dist_S[(hu$dist_S!=0)])
w1  #x-coord where the jump occurs
h1<-unique(hu$S)
h1  #y-coord where the jump occurs
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
area_S

area_S==hu$Au_S  # it's a check

hu$Au_Si

#P stat value for upper tail
(area_S-hu$Au_Si)==hu$abs_res

#Test for when two parallel boundary lines are on opposite sides of vi+vj=1 line
lb=0.3
ub=0.8

@@

#calculate the area under the curve 
w1<-unique(hm$dist_S[(hm$dist_S!=0)])
w1  #x-coord where the jump occurs
h1<-unique(hm$S)
h1  #y-coord where the jump occurs
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
area_S

area_S==hm$Au_S # it's a check

hm$Au_Si

#P stat value for middle section
(area_S-hm$Au_Si)==hm$abs_res
```

@@

Test for unbiased estimator of third central moment:
```{r test_myskewness, echo=T, cache=T, cache.extra=list(mtime("SkewnessAnd3CentMom.R"))}
source("SkewnessAnd3CentMom.R")
set.seed(101)

@@

x<-rpois(100000,5)
my3cm(x) #should be close to 5, but not necessarily super close
#since 3rd moments are hard to estimate accurately

@@

Test the copsurrog2d function:
```{r test_copsurrog2d, echo=T}
library("VineCopula")
source("copsurrog2d.R")
set.seed(101)

@@

Test copsurrog2d to see whether changing the copula
markedly influences the distribution
of the spatial mean:
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
set.seed(101)

@@

Test the ncsurrog function:
```{r test_ncsurrog, echo=T, cache=T, cache.extra=list(mtime("ncsurrog.R"))}
source("ncsurrog.R")
set.seed(103)

>>>>

# Test flexible copula functions
We here test the functions `Corbds`, `Pbds` and `D2bds`.

@@

Test the `Corbds` function:
```{r test_copula_function_flexible_cor, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
plot_vivj(vi,vj,lb,ub)
h<-Corbds(vi,vj,lb=lb,ub=ub)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

@@

Test the `D2bds` function:
```{r test_copula_function_flexible_D2, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-D2bds(vi,vj,lb=lb,ub=ub)
if (abs((sum(ep[1:4]^2)/2)-h)<1e-12)
{
  print("passed")
}
```

Test the `Pbds` function:
```{r test_copula_function_flexible_P, echo=T}
source("CopulaFunctions_flexible.R")

@@

#Test the case in which the two parallel boundary lines are on the left side 
#of the vi+vj=1 line
lb=0
ub=.45
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)
hl<-Pbds(vi,vj,lb=lb,ub=ub)

#plot the step function output - should have one jump at a small distance
#due to the one data point that is between the bound lines
plot(hl$dist_S,hl$S,type="b")

#calculate the area under the curve, compare to what the function returns 
vertices<-unique(hl$dist_S[(hl$dist_S!=0)])
area_S<-(vertices[2]-vertices[1])*1
if (abs(area_S-hl$Au_S)<1e-12)
{
  print("passed")
} else
{
  print("Au_S incorrectly computed")
}

#check P stat value for lower tail
if (abs(area_S-hl$Au_Si-hl$abs_res)<1e-12)
{
  print("passed")
} else
{
  print("Error in Pbds, the P stat")
}

#Test the case in which the two parallel boundary lines are on the right side 
#of the vi+vj=1 line
lb=0
ub=.45 
plot_vivj(vi=vi,vj=vj,lb=(1-ub),ub=(1-lb))

@@

#hl$Au_Si should be the same as hu$Au_Si
if (abs(hl$Au_Si-hu$Au_Si)<1e-12)
{
  print("passed")
}else
{
  print("Error in Pbds, Au_Si")
}

#plot the step fn - should have two jumps
plot(hu$dist_S,hu$S,type="b")

#calculate the area under the curve 
w1<-unique(hu$dist_S[(hu$dist_S!=0)])
w1  #x-coords where the jumps occur, and the max dist
h1<-unique(hu$S)
h1  #y-coords of the above points
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
if (abs(area_S-hu$Au_S)<1e-12)  
{
  print("passed")
} else
{
  print("Au_S incorrectly computed")
}

#P stat value for upper tail
if (abs(area_S-hu$Au_Si-hu$abs_res)<1e-12)
{
  print("passed")
}else
{
  print("P stat incorrectly computed")
}

#Test for the case in which the two parallel boundary lines are on opposite 
#sides of vi+vj=1 line
lb<-0.28
ub<-0.8

@@

#calculate the area under the curve 
w1<-unique(hm$dist_S[(hm$dist_S!=0)])
w1  #x-coord where the jump occurs
h1<-unique(hm$S)
h1  #y-coord where the jump occurs
area_S<-((w1[2]-w1[1])*(h1[2]-h1[1]))+((w1[3]-w1[2])*(h1[3]-h1[1]))
if (abs(area_S-hm$Au_S)<1e-12) 
{
  print("passed")
}else
{
  print("Error")
}

#P stat value for middle section
if (abs(area_S-hm$Au_Si-hm$abs_res)<1e-12)
{
  print("passed")
}else
{
  print("Error")
}
```

@@

We here test the function `my3cm`, which is an unbiased estimator of the 3rd central moment:
```{r test_myskewness, echo=T, cache=T, cache.extra=list(mtime("SkewnessAnd3CentMom.R"))}
source("SkewnessAnd3CentMom.R")
set.seed(101)

@@

x<-rpois(100000,5)
#should be close to 5, but not necessarily super close
#since 3rd moments are hard to estimate accurately
my3cm(x)

@@

Test the `copsurrog2d` function:
```{r test_copsurrog2d, echo=T}
library("VineCopula")
source("copsurrog2d.R")
set.seed(101)

@@

Test `copsurrog2d` to see whether changing the copula
markedly influences the distribution
of the spatial mean:
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
set.seed(101)

@@

Test the `ncsurrog` function:
```{r test_ncsurrog, echo=T, cache=T, cache.extra=list(mtime("ncsurrog.R"))}
source("ncsurrog.R")
set.seed(103)
